An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-27 paper/6.related-work.tex
update tex 20191125
- def of get_mh
- v / v'
- experiments: xpg is faster than pgs
- dummy
- kpg: lazy eval on fi-cond
- figure size
- typos
major update

\subsubsection*{BX langauges and implementations}

There are many BX languages \cite{josh_pepm} \cite{BXtend} \cite{eMoflon} \cite{EVL+Strace} \cite{JTL} \cite{NMF}
%(memo: BXtend, eMoflon, EVL+Strace, JTL, NMF. SDMLib should be added?)
based on several application scenarios and BX lenses works \cite{} (add papers for lenses). The semantics and correctness of bidirectional programs has been investigated intensively during the past years, but their efficiency and optimization are not yet fully understood. Anjorin et. al. introduces the first benchmark for BX languages and compared them \cite{BXcomp}. However, the improvement for practical implementation of BX languages is still missing. As a first step, we study different evaluation methods to optimized their evaluation. We can say this paper will be first attempt to improve efficiency of BX composition evaluation. In this paper we focus on a BX language BiGUL \cite{josh_pepm} \cite{josh_popl}, we compare BiGUL's method (in Section 1) and our methods (in Section 3 and 4). From experimental results, we find that there is no best approach for all BX programs. It is important to choose good method depending on the BX programs and their inputs. In this paper we focus on BiGUL, however our methods can be applicable to other BX languages which have similar problems.
% its implementation uses ``not keeping any intermediate states and obtaining them by evaluation when they are needed'' strategy. Other BX languages might have the same problem, and our approach can be applicable.

@@

In this paper, we use several optimization techniques: tupling, lazy update, and lazy computation (\textcolor{red}{also fusion?}).

Tupling \cite{tupling} is an optimization technique by combining several computations. Although tupling is usually used for reducing the evaluation cost\cite{}, we use it to reduce the size of the things need to keep.

We introduce lazy update to remove repeated evaluation of put. This is different from lazy evaluation. In lazy evaluation we have everything that is needed to evaluate. In our lazy update, because view information is missing, we postpone the evaluation. (\textcolor{red}{Relation between delta lenses?})

Lazy evaluation \cite{} is well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

>>>>

\subsubsection*{BX languages and implementations}

There are many BX languages \cite{josh_pepm} \cite{BXtend} \cite{eMoflon} \cite{EVL+Strace} \cite{JTL} \cite{NMF}
%(memo: BXtend, eMoflon, EVL+Strace, JTL, NMF. SDMLib should be added?)
based on several application scenarios and BX lenses works \cite{} (add papers for lenses). The semantics and correctness of bidirectional programs has been investigated intensively during the past years, but their efficiency and optimization are not yet fully understood. Anjorin et. al. introduces the first benchmark for BX languages and compared them \cite{BXcomp}. However, the improvement for practical implementation of BX languages is still missing. As a first step, we study different evaluation methods to optimized their evaluation. We can say this paper will be first attempt to improve efficiency of BX composition evaluation. In this paper we focus on a BX language BiGUL \cite{josh_pepm} \cite{josh_popl}, we compare BiGUL's method (in Section 2) and our methods (in Section 3 and 4). From experimental results of left associative programs, we know that our memoization methods are faster than the original BiGUL's evaluation method.
In this paper we focus on BiGUL, however our methods can be applicable to other BX languages which have similar problems.

%find that there is no best approach for all BX programs. It is important to choose good method depending on the BX programs and their inputs. 
% its implementation uses ``not keeping any intermediate states and obtaining them by evaluation when they are needed'' strategy. Other BX languages might have the same problem, and our approach can be applicable.

@@

Memoization \cite{} is well-known technique to reduce extra evaluation. In our case, simple application of memoization $put_m$ works well for many BX programs.
Another way to reduce extra evaluation is fusion \cite{}. However, fusion of BX programs are not considered well \textcolor{red}{(really?)}. Therefore we do not use this way.
  Instead of that, we introduce another way: using tupling \cite{}, lazy update and lazy computation \cite{}. Tupling \cite{tupling} is often used for reducint common evaluations, but we use it for reducing the size of complements.
  Lazy evaluation \cite{} is also a well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

%In this paper, we use several well-known techniques: tupling, lazy update, and lazy computation (\textcolor{red}{also fusion?}).

%Tupling \cite{tupling} is an optimization technique by combining several computations. Although tupling is usually used for reducing the evaluation cost\cite{}, we use it to reduce the size of the things need to keep.

%We introduce lazy update to remove repeated evaluation of put. This is different from lazy evaluation. In lazy evaluation we have everything that is needed to evaluate. In our lazy update, because view information is missing, we postpone the evaluation. (\textcolor{red}{Relation between delta lenses?})

%Lazy evaluation \cite{} is well-known and widly-used optimization technique to reduce the redundant evaluation. Because we use OCaml for implementation, we need to introduce this explicitly. If we use Haskell, a lazy evaluated language, we do not need to introduce them.

### 2019-11-27 paper/7.conclusion.tex
major update

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results, we know that there is no best approach for all BX programs. However, if programmer can choose one method based on the BX programs and inputs, we can use better evaluation methods.

We will continue our work on the following points. First is extention of our language. Currently, because $pg$ requires very-well-behaved property

\begin{itemize}
\item overcome our limitations
  \begin{itemize}
  \item very-well-behaved $\to$ only xpg?
  \item In case expressions, path's problem $\to$ only xpg?
  \item How to obtain $\to$ only xpg?
  \end{itemize}
  \item tests for big BX programs
\item Type system \& Typing -- for safety
\end{itemize}

>>>>

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative composition of BX programs, we know that $put_m$ is fastest method if input size is not very big and $xpg$ is fastest for other left associative programs.
This shows that if programmer choose one method based on the their BX programs and inputs, they can use efficient evaluation.

%there is no best approach for all BX programs. However, if programmer can choose one method based on the BX programs and inputs, we can use better evaluation methods.

We will continue our work on the following points.
First is overcomming our limitation in $xpg$. In $xpg$, there are several limitations: only very-well-behaved programs, path problem (shown in Section ..). To be a practical evlauation method, extention is needed. After extention of the language, we can evaluate more interesting programs for experimental results.

Second is analysis about BX programs and inputs to choose the best evaluation method automatically.
Currently, programmers have to choose the evaluation method by themselves based on their BX programs and inputs. If automatic choice is possible, we can reduce programmer's burden.

\begin{itemize}
\item construct\_dummy?
\end{itemize}

%First is extention of our language. Currently, because $pg$ requires very-well-behaved property

%\begin{itemize}
%\item overcome our limitations
%  \begin{itemize}
%  \item very-well-behaved $\to$ only xpg?
%  \item In case expressions, path's problem $\to$ only xpg?
%  \item How to obtain $\to$ only xpg?
%  \end{itemize}
%  \item tests for big BX programs
%  \item Type system \& Typing -- for safety
%  \item analysis about programs/inputs to choose the best method automatically
%\end{itemize}
